Testing for Measurement Invariance with Respect to an Ordinal Variable

### 2014-11-12 ordinal/preprint.Rnw
added final publication info
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@360 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% publication info and copyright notice
\usepackage{fancyhdr}
\setlength{\headheight}{15pt}
\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\thispagestyle{plain}
\fancyhf{}
\fancyhead[RO,LE]{\thepage}
\fancyhead[CO]{\textit{\normalsize Edgar C. Merkle, Jinyan Fan, Achim Zeileis}}
\fancyhead[CE]{\textit{\normalsize Testing for Ordinal Measurement Invariance}}
\fancyfoot[LO,LE]{\small Copyright {\copyright} 2013 The Psychometric Society}
\fancypagestyle{plain}{
\fancyhf{}
\fancyfoot[LO,LE]{\small This is a preprint of an article accepted for publication in \textit{Psychometrika}.\\ %%, \textbf{78}(1), 59--82.\\
  Copyright~{\copyright} 2013 The Psychometric Society \url{http://www.psychometrika.org/}}
  %% \doi{10.1007/S11336-012-9302-4}}
}

>>>>

%% publication info and copyright notice
\usepackage{fancyhdr}
\setlength{\headheight}{15pt}
\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\thispagestyle{plain}
\fancyhf{}
\fancyhead[RO,LE]{\thepage}
\fancyhead[CO]{\textit{\normalsize Edgar C. Merkle, Jinyan Fan, Achim Zeileis}}
\fancyhead[CE]{\textit{\normalsize Testing for Ordinal Measurement Invariance}}
\fancyfoot[LO,LE]{\small Copyright {\copyright} 2013 The Psychometric Society}
\fancypagestyle{plain}{
\fancyhf{}
\fancyfoot[LO,LE]{\small This is a preprint of an article published in \textit{Psychometrika}, \textbf{79}(4), 569--584.\\
  Copyright~{\copyright} 2013 The Psychometric Society \url{http://www.psychometrika.org/}\\
  \doi{10.1007/S11336-013-9376-7}}
}
